Proposed Solution

### 2016-01-29 intro1.tex
starting

Configuration errors are one of the most important root-causes of 
modern software system failures~\cite{xu15systems,yin11anempirical}. 
In practice, misconfiguration problems may result in 
security vulnerabilities,
application crashes, severe disruptions in software functionality,
and incorrect program executions%
~\cite{xu15systems,zhang14encore,yuan11context}.
Although several efforts have been proposed to automate configuration
error diagnosis after failures occur%
~\cite{wang04automatic,attariyan10automating,%
su07autobash,whitaker04configuration}, 
they rely on manual ways to understand and detect the failure symptoms.
Such solutions typically incur high administration cost (\eg, 
requiring users to write pattern-matching scripts) 
and are unreliable (\eg, some errors may show no user-visible symptoms).
These shortcomings often lead to prolonged delays between
the occurrence and the detection of errors, thus causing unrecoverable
damage to system states.

>>>>

Configuration errors are one of the most important root-causes of 
modern software system failures~\cite{xu15systems,yin11anempirical}. 
In practice, misconfiguration problems may result in 
security vulnerabilities,
application crashes, severe disruptions in software functionality,
and incorrect program executions%
~\cite{xu15systems,zhang14encore,yuan11context}.
Although several tools have been proposed to automate configuration
error diagnosis after failures occur%
~\cite{wang04automatic,attariyan10automating,%
su07autobash,whitaker04configuration}, 
these tools rely on manual ways to understand and detect the failure symptoms. The main reason for this approach ... \ruzica{Ennan, can you talk here how usually config files look, only untyped assigments}

Such solutions typically incur high administration cost (\eg, 
requiring users to write pattern-matching scripts) 
and are unreliable (\eg, some errors may show no user-visible symptoms).
These shortcomings often lead to prolonged delays between
the occurrence and the detection of errors, thus causing unrecoverable
damage to system states.
